BERT Model Compression and Weight Sharing

### 2019-05-12 paper/paper.tex
Wording change in KD section

To provide a concrete example of how this might work, suppose BERT captures
from its pre-training that ``bad'', ``horrible,'' and ``terrible'' are
approximate synonyms. In a sentiment task, these three words appear in three
different sentences, two of which are negative, and one of which is positive.
A fine-tuned BERT may provide a lower likelihood of being positive to the
positive sentence than it would otherwise even if the word of interest appears
nowhere else.

>>>>

To provide a concrete example of how this might work, suppose BERT captures
from its pre-training that ``bad'', ``horrible,'' and ``terrible'' are
approximate synonyms. In a sentiment task, these three words appear in three
different sentences, two of which are negative, and one of which is positive.
A fine-tuned BERT may predict a lower likelihood of being positive to the
positive sentence than it would otherwise even if the word of interest appears
nowhere else.
